---
title: "TRhizo-localAdaptation"
subtitle: "Local Adaptation by Urbanization"
author: "David Murray-Stoker"
output:
  pdf_document:
    toc: true
    toc_depth: 4
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(knitr.graphics.error = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
kableExtra::usepackage_latex("float")
```

```{r Load Packages for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```





\newpage
# Load Packages & Data

```{r Load Packages & Data, echo = TRUE, results = "hide"}
## Load the tidyverse
library(tidyverse)

## Load packages for data analysis
library(broom)
library(easystats)

## Read in data
# Urbanization data
urbanization.data <- read_rds(file = "data/full_urbanization_data.rds")
# Local adaptation indices
load("data_analysis/4-local_adaptation_indices/local_adaptation_indices.RData")

## Set function for scaling variables
center_and_scale <- function(x) {
  (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
}
```





\newpage
# Data Management

```{r Data Management, echo = TRUE}
## Aboveground biomass
# Global index
aboveground.biomass.LA.global.combined.data <- aboveground.biomass.LA.global.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
# Rural index
aboveground.biomass.LA.rural.combined.data <- aboveground.biomass.LA.rural.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
# Urban index
aboveground.biomass.LA.urban.combined.data <- aboveground.biomass.LA.urban.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )

## Belowground biomass
# Global index
belowground.biomass.LA.global.combined.data <- belowground.biomass.LA.global.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
# Rural index
belowground.biomass.LA.rural.combined.data <- belowground.biomass.LA.rural.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
# Urban index
belowground.biomass.LA.urban.combined.data <- belowground.biomass.LA.urban.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )

## Nodule density
# Global index
nodule.density.LA.global.combined.data <- nodule.density.LA.global.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
# Rural index
nodule.density.LA.rural.combined.data <- nodule.density.LA.rural.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
# Urban index
nodule.density.LA.urban.combined.data <- nodule.density.LA.urban.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )

## Fixing nodule density
fixing.nodule.density.LA.global.combined.data <- fixing.nodule.density.LA.global.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
# Rural index
fixing.nodule.density.LA.rural.combined.data <- fixing.nodule.density.LA.rural.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
# Urban index
fixing.nodule.density.LA.urban.combined.data <- fixing.nodule.density.LA.urban.data %>%
  left_join(urbanization.data, by = "Population") %>%
  drop_na() %>%
  type_convert(col_types = c("ffnnnnnfnin")) %>%
  mutate(
    Distance_Scaled = center_and_scale(Distance),
    Human_Influence_Index_Scaled = center_and_scale(Human_Influence_Index),
    Mean_ISC_Scaled = center_and_scale(Mean_ISC)
  )
```


```{r Save Final Workspace, include = FALSE}
save.image("data_analysis/6-local_adaptation_by_urbanization/local_adaptation_by_urbanization_data.RData")
```





\newpage
# Aboveground Biomass Regressions

## Global Index

### Fit the Regressions

```{r Fit the Regressions: Aboveground Biomass Global Index, echo = TRUE}
## Distance
aboveground.biomass.by.distance.global.LM <- lm(
  AG_Biomass_LA_Global ~ Distance_Scaled,
  data = aboveground.biomass.LA.global.combined.data
)

## Human influence index
aboveground.biomass.by.HII.global.LM <- lm(
  AG_Biomass_LA_Global ~ Human_Influence_Index_Scaled,
  data = aboveground.biomass.LA.global.combined.data
)

## Impervious surface cover
aboveground.biomass.by.ISC.global.LM <- lm(
  AG_Biomass_LA_Global ~ Mean_ISC_Scaled,
  data = aboveground.biomass.LA.global.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Aboveground Biomass Global Index, echo = TRUE, eval = FALSE}
## Distance
check_model(aboveground.biomass.by.distance.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(aboveground.biomass.by.HII.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(aboveground.biomass.by.ISC.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Aboveground Biomass Global Index (Distance), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.distance.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass global local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Aboveground Biomass Global Index (HII), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.HII.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass global local adaptation index by HII model. Adjusted R-squared = 0.031.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Aboveground Biomass Global Index (ISC), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.ISC.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass global local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Rural Index

### Fit the Regressions

```{r Fit the Regressions: Aboveground Biomass Rural Index, echo = TRUE}
## Distance
aboveground.biomass.by.distance.rural.LM <- lm(
  AG_Biomass_LA_Rural ~ Distance_Scaled,
  data = aboveground.biomass.LA.rural.combined.data
)

## Human influence index
aboveground.biomass.by.HII.rural.LM <- lm(
  AG_Biomass_LA_Rural ~ Human_Influence_Index_Scaled,
  data = aboveground.biomass.LA.rural.combined.data
)

## Impervious surface cover
aboveground.biomass.by.ISC.rural.LM <- lm(
  AG_Biomass_LA_Rural ~ Mean_ISC_Scaled,
  data = aboveground.biomass.LA.rural.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Aboveground Biomass Rural Index, echo = TRUE, eval = FALSE}
## Distance
check_model(aboveground.biomass.by.distance.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(aboveground.biomass.by.HII.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(aboveground.biomass.by.ISC.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Aboveground Biomass Rural Index (Distance), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.distance.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass rural local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Aboveground Biomass Rural Index (HII), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.HII.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass rural local adaptation index by HII model. Adjusted R-squared = 0.012.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Aboveground Biomass Rural Index (ISC), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.ISC.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass rural local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Urban Index

### Fit the Regressions

```{r Fit the Regressions: Aboveground Biomass Urban Index, echo = TRUE}
## Distance
aboveground.biomass.by.distance.urban.LM <- lm(
  AG_Biomass_LA_Urban ~ Distance_Scaled,
  data = aboveground.biomass.LA.urban.combined.data
)

## Human influence index
aboveground.biomass.by.HII.urban.LM <- lm(
  AG_Biomass_LA_Urban ~ Human_Influence_Index_Scaled,
  data = aboveground.biomass.LA.urban.combined.data
)

## Impervious surface cover
aboveground.biomass.by.ISC.urban.LM <- lm(
  AG_Biomass_LA_Urban ~ Mean_ISC_Scaled,
  data = aboveground.biomass.LA.urban.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Aboveground Biomass Urban Index, echo = TRUE, eval = FALSE}
## Distance
check_model(aboveground.biomass.by.distance.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(aboveground.biomass.by.HII.urban.LM)
# Linear assumption met
# Slight (+ non-concerning) heterogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(aboveground.biomass.by.ISC.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Aboveground Biomass Urban Index (Distance), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.distance.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass urban local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Aboveground Biomass Urban Index (HII), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.HII.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass urban local adaptation index by HII model. Adjusted R-squared = 0.022.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Aboveground Biomass Urban Index (ISC), echo = FALSE}
kable(
  tidy(summary(aboveground.biomass.by.ISC.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the aboveground biomass urban local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Belowground Biomass Regressions

## Global Index

### Fit the Regressions

```{r Fit the Regressions: Belowground Biomass Global Index, echo = TRUE}
## Distance
belowground.biomass.by.distance.global.LM <- lm(
  BG_Biomass_LA_Global ~ Distance_Scaled,
  data = belowground.biomass.LA.global.combined.data
)

## Human influence index
belowground.biomass.by.HII.global.LM <- lm(
  BG_Biomass_LA_Global ~ Human_Influence_Index_Scaled,
  data = belowground.biomass.LA.global.combined.data
)

## Impervious surface cover
belowground.biomass.by.ISC.global.LM <- lm(
  BG_Biomass_LA_Global ~ Mean_ISC_Scaled,
  data = belowground.biomass.LA.global.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Belowground Biomass Global Index, echo = TRUE, eval = FALSE}
## Distance
check_model(belowground.biomass.by.distance.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(belowground.biomass.by.HII.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(belowground.biomass.by.ISC.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Belowground Biomass Global Index (Distance), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.distance.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass global local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Belowground Biomass Global Index (HII), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.HII.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass global local adaptation index by HII model. Adjusted R-squared = 0.012.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Belowground Biomass Global Index (ISC), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.ISC.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass global local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Rural Index

### Fit the Regressions

```{r Fit the Regressions: Belowground Biomass Rural Index, echo = TRUE}
## Distance
belowground.biomass.by.distance.rural.LM <- lm(
  BG_Biomass_LA_Rural ~ Distance_Scaled,
  data = belowground.biomass.LA.rural.combined.data
)

## Human influence index
belowground.biomass.by.HII.rural.LM <- lm(
  BG_Biomass_LA_Rural ~ Human_Influence_Index_Scaled,
  data = belowground.biomass.LA.rural.combined.data
)

## Impervious surface cover
belowground.biomass.by.ISC.rural.LM <- lm(
  BG_Biomass_LA_Rural ~ Mean_ISC_Scaled,
  data = belowground.biomass.LA.rural.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Belowground Biomass Rural Index, echo = TRUE, eval = FALSE}
## Distance
check_model(belowground.biomass.by.distance.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(belowground.biomass.by.HII.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(belowground.biomass.by.ISC.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Belowground Biomass Rural Index (Distance), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.distance.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass rural local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Belowground Biomass Rural Index (HII), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.HII.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass rural local adaptation index by HII model. Adjusted R-squared = 0.024.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Belowground Biomass Rural Index (ISC), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.ISC.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass rural local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Urban Index

### Fit the Regressions

```{r Fit the Regressions: Belowground Biomass Urban Index, echo = TRUE}
## Distance
belowground.biomass.by.distance.urban.LM <- lm(
  BG_Biomass_LA_Urban ~ Distance_Scaled,
  data = belowground.biomass.LA.urban.combined.data
)

## Human influence index
belowground.biomass.by.HII.urban.LM <- lm(
  BG_Biomass_LA_Urban ~ Human_Influence_Index_Scaled,
  data = belowground.biomass.LA.urban.combined.data
)

## Impervious surface cover
belowground.biomass.by.ISC.urban.LM <- lm(
  BG_Biomass_LA_Urban ~ Mean_ISC_Scaled,
  data = belowground.biomass.LA.urban.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Belowground Biomass Urban Index, echo = TRUE, eval = FALSE}
## Distance
check_model(belowground.biomass.by.distance.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(belowground.biomass.by.HII.urban.LM)
# Linear assumption met
# Slight (+ non-concerning) heterogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(belowground.biomass.by.ISC.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Belowground Biomass Urban Index (Distance), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.distance.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass urban local adaptation index by distance model. Adjusted R-squared = 0.001.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Belowground Biomass Urban Index (HII), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.HII.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass urban local adaptation index by HII model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Belowground Biomass Urban Index (ISC), echo = FALSE}
kable(
  tidy(summary(belowground.biomass.by.ISC.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the belowground biomass urban local adaptation index by ISC model. Adjusted R-squared = 0.022.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Nodule Density Regressions

## Global Index

### Fit the Regressions

```{r Fit the Regressions: Nodule Density Global Index, echo = TRUE}
## Distance
nodule.density.by.distance.global.LM <- lm(
  Nod_Density_LA_Global ~ Distance_Scaled,
  data = nodule.density.LA.global.combined.data
)

## Human influence index
nodule.density.by.HII.global.LM <- lm(
  Nod_Density_LA_Global ~ Human_Influence_Index_Scaled,
  data = nodule.density.LA.global.combined.data
)

## Impervious surface cover
nodule.density.by.ISC.global.LM <- lm(
  Nod_Density_LA_Global ~ Mean_ISC_Scaled,
  data = nodule.density.LA.global.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Nodule Density Global Index, echo = TRUE, eval = FALSE}
## Distance
check_model(nodule.density.by.distance.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(nodule.density.by.HII.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(nodule.density.by.ISC.global.LM)
# Linear assumption met
# Slight (+ non-concerning) heterogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Nodule Density Global Index (Distance), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.distance.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density global local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Nodule Density Global Index (HII), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.HII.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density global local adaptation index by HII model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Nodule Density Global Index (ISC), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.ISC.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density global local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Rural Index

### Fit the Regressions

```{r Fit the Regressions: Nodule Density Rural Index, echo = TRUE}
## Distance
nodule.density.by.distance.rural.LM <- lm(
  Nod_Density_LA_Rural ~ Distance_Scaled,
  data = nodule.density.LA.rural.combined.data
)

## Human influence index
nodule.density.by.HII.rural.LM <- lm(
  Nod_Density_LA_Rural ~ Human_Influence_Index_Scaled,
  data = nodule.density.LA.rural.combined.data
)

## Impervious surface cover
nodule.density.by.ISC.rural.LM <- lm(
  Nod_Density_LA_Rural ~ Mean_ISC_Scaled,
  data = nodule.density.LA.rural.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Nodule Density Rural Index, echo = TRUE, eval = FALSE}
## Distance
check_model(nodule.density.by.distance.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(nodule.density.by.HII.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(nodule.density.by.ISC.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Nodule Density Rural Index (Distance), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.distance.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density rural local adaptation index by distance model. Adjusted R-squared = 0.006.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Nodule Density Rural Index (HII), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.HII.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density rural local adaptation index by HII model. Adjusted R-squared = 0.014.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Nodule Density Rural Index (ISC), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.ISC.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density rural local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Urban Index

### Fit the Regressions

```{r Fit the Regressions: Nodule Density Urban Index, echo = TRUE}
## Distance
nodule.density.by.distance.urban.LM <- lm(
  Nod_Density_LA_Urban ~ Distance_Scaled,
  data = nodule.density.LA.urban.combined.data
)

## Human influence index
nodule.density.by.HII.urban.LM <- lm(
  Nod_Density_LA_Urban ~ Human_Influence_Index_Scaled,
  data = nodule.density.LA.urban.combined.data
)

## Impervious surface cover
nodule.density.by.ISC.urban.LM <- lm(
  Nod_Density_LA_Urban ~ Mean_ISC_Scaled,
  data = nodule.density.LA.urban.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Nodule Density Urban Index, echo = TRUE, eval = FALSE}
## Distance
check_model(nodule.density.by.distance.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(nodule.density.by.HII.urban.LM)
# Linear assumption met
# Slight (+ non-concerning) heterogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(nodule.density.by.ISC.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Nodule Density Urban Index (Distance), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.distance.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density urban local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Nodule Density Urban Index (HII), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.HII.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density urban local adaptation index by HII model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Nodule Density Urban Index (ISC), echo = FALSE}
kable(
  tidy(summary(nodule.density.by.ISC.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the nodule density urban local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Fixing Nodule Density Regressions

## Global Index

### Fit the Regressions

```{r Fit the Regressions: Fixing Nodule Density Global Index, echo = TRUE}
## Distance
fixing.nodule.density.by.distance.global.LM <- lm(
  Fix_Nod_Density_LA_Global ~ Distance_Scaled,
  data = fixing.nodule.density.LA.global.combined.data
)

## Human influence index
fixing.nodule.density.by.HII.global.LM <- lm(
  Fix_Nod_Density_LA_Global ~ Human_Influence_Index_Scaled,
  data = fixing.nodule.density.LA.global.combined.data
)

## Impervious surface cover
fixing.nodule.density.by.ISC.global.LM <- lm(
  Fix_Nod_Density_LA_Global ~ Mean_ISC_Scaled,
  data = fixing.nodule.density.LA.global.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Fixing Nodule Density Global Index, echo = TRUE, eval = FALSE}
## Distance
check_model(fixing.nodule.density.by.distance.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(fixing.nodule.density.by.HII.global.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(fixing.nodule.density.by.ISC.global.LM)
# Linear assumption met
# Slight (+ non-concerning) heterogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Fixing Nodule Density Global Index (Distance), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.distance.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density global local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Fixing Nodule Density Global Index (HII), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.HII.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density global local adaptation index by HII model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Fixing Nodule Density Global Index (ISC), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.ISC.global.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density global local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Rural Index

### Fit the Regressions

```{r Fit the Regressions: Fixing Nodule Density Rural Index, echo = TRUE}
## Distance
fixing.nodule.density.by.distance.rural.LM <- lm(
  Fix_Nod_Density_LA_Rural ~ Distance_Scaled,
  data = fixing.nodule.density.LA.rural.combined.data
)

## Human influence index
fixing.nodule.density.by.HII.rural.LM <- lm(
  Fix_Nod_Density_LA_Rural ~ Human_Influence_Index_Scaled,
  data = fixing.nodule.density.LA.rural.combined.data
)

## Impervious surface cover
fixing.nodule.density.by.ISC.rural.LM <- lm(
  Fix_Nod_Density_LA_Rural ~ Mean_ISC_Scaled,
  data = fixing.nodule.density.LA.rural.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Fixing Nodule Density Rural Index, echo = TRUE, eval = FALSE}
## Distance
check_model(fixing.nodule.density.by.distance.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(fixing.nodule.density.by.HII.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(fixing.nodule.density.by.ISC.rural.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Fixing Nodule Density Rural Index (Distance), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.distance.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density rural local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Fixing Nodule Density Rural Index (HII), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.HII.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density rural local adaptation index by HII model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Fixing Nodule Density Rural Index (ISC), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.ISC.rural.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density rural local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Urban Index

### Fit the Regressions

```{r Fit the Regressions: Fixing Nodule Density Urban Index, echo = TRUE}
## Distance
fixing.nodule.density.by.distance.urban.LM <- lm(
  Fix_Nod_Density_LA_Urban ~ Distance_Scaled,
  data = fixing.nodule.density.LA.urban.combined.data
)

## Human influence index
fixing.nodule.density.by.HII.urban.LM <- lm(
  Fix_Nod_Density_LA_Urban ~ Human_Influence_Index_Scaled,
  data = fixing.nodule.density.LA.urban.combined.data
)

## Impervious surface cover
fixing.nodule.density.by.ISC.urban.LM <- lm(
  Fix_Nod_Density_LA_Urban ~ Mean_ISC_Scaled,
  data = fixing.nodule.density.LA.urban.combined.data
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Fixing Nodule Density Urban Index, echo = TRUE, eval = FALSE}
## Distance
check_model(fixing.nodule.density.by.distance.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Human influence index
check_model(fixing.nodule.density.by.HII.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution

## Impervious surface cover
check_model(fixing.nodule.density.by.ISC.urban.LM)
# Linear assumption met
# Homogeneity of variance
# Residuals approximately follow a normal distribution
```

\newpage

### Model Summaries

```{r Model Summary: Fixing Nodule Density Urban Index (Distance), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.distance.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density urban local adaptation index by distance model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Fixing Nodule Density Urban Index (HII), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.HII.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density urban local adaptation index by HII model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Model Summary: Fixing Nodule Density Urban Index (ISC), echo = FALSE}
kable(
  tidy(summary(fixing.nodule.density.by.ISC.urban.LM)),
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the fixing nodule density urban local adaptation index by ISC model. Adjusted R-squared = ~0.",
  col.names = c("Term", "Estimate", "SE", "t", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





```{r Save the Workspace, include = FALSE}
save.image("data_analysis/6-local_adaptation_by_urbanization/local_adaptation_by_urbanization_data.RData")
```









\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages,
  booktabs = TRUE,
  caption = "Packages required for data management and analysis."
) %>%
  kable_styling(
    full_width = FALSE,
    latex_options = c("HOLD_position", "striped")
  )
```
