---
title: "TRhizo-localAdaptation"
subtitle: "Local Adaptation Indices"
author: "David Murray-Stoker"
output:
  pdf_document:
    toc: true
    toc_depth: 4
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(knitr.graphics.error = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
kableExtra::usepackage_latex("float")
```

```{r Load Packages for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```





\newpage
# Load Packages & Data

```{r Load Packages & Data, echo = TRUE, results = "hide"}
## Load the tidyverse
library(tidyverse)

## Packages for analysis
library(broom)
library(lme4)
library(lmerTest)

## Read in data
biomass.data <- read_rds(file = "data/cleaned_biomass_data.rds")
nodule.data  <- read_rds(file = "data/cleaned_nodule_data.rds")
```





\newpage
# Linear Mixed Effects Models

```{r Fit Linear Mixed Effects Models, echo = TRUE}
## Aboveground biomass
aboveground.biomass.LA.LMM <- lmer(
  sqrt(Aboveground_Biomass) ~ Microbiome * Nitrogen
    + (1 | Microbiome:Population)
    + (1 | Nitrogen:Population)
    + (1 | Microbiome:Nitrogen:Population)
    + (1 | Population)
    + (1 | Block),
  data = biomass.data,
  REML = TRUE
)

## Belowground biomass
belowground.biomass.LA.LMM <- lmer(
  sqrt(Belowground_Biomass) ~ Microbiome * Nitrogen
    + (1 | Microbiome:Population)
    + (1 | Nitrogen:Population)
    + (1 | Microbiome:Nitrogen:Population)
    + (1 | Population)
    + (1 | Block),
  data = biomass.data,
  REML = TRUE
)

## Nodule density
nodule.density.LA.LMM <- lmer(
  log(Nodule_Density + 1) ~ Microbiome * Nitrogen
    + (1 | Microbiome:Population)
    + (1 | Nitrogen:Population)
    + (1 | Microbiome:Nitrogen:Population)
    + (1 | Population)
    + (1 | Block),
  data = nodule.data,
  REML = TRUE
)

## Fixing nodule density
fixing.nodule.density.LA.LMM <- lmer(
  log(Fixing_Nodule_Density + 1) ~ Microbiome * Nitrogen
    + (1 | Microbiome:Population)
    + (1 | Nitrogen:Population)
    + (1 | Microbiome:Nitrogen:Population)
    + (1 | Population)
    + (1 | Block),
  data = nodule.data,
  REML = TRUE
)
```





\newpage
# Best Linear Unbiased Predictors (BLUPs)

```{r calculate_MxNxP_BLUPs Functions, echo = TRUE}
## Set the calculate_MxNxP_BLUPs function
calculate_MxNxP_BLUPs <- function(lme4_model) {
  ranef(lme4_model)$`Microbiome:Nitrogen:Population` %>%
    tibble::rownames_to_column("Microbiome_Nitrogen_Population") %>%
    dplyr::rename(Estimate = 2)
}
```

\vspace{10pt}

```{r Get BLUPs from LMMs, echo = TRUE}
## Aboveground biomass
aboveground.biomass.uncleaned.BLUPs <- calculate_MxNxP_BLUPs(
  aboveground.biomass.LA.LMM
) %>%
  separate(
    col = Microbiome_Nitrogen_Population,
    c("Microbiome", "Nitrogen", "Population"),
    sep = ":"
  )

## Belowground biomass
belowground.biomass.uncleaned.BLUPs <- calculate_MxNxP_BLUPs(
  belowground.biomass.LA.LMM
) %>%
  separate(
    col = Microbiome_Nitrogen_Population,
    c("Microbiome", "Nitrogen", "Population"),
    sep = ":"
  )

## Nodule density
nodule.density.uncleaned.BLUPs <- calculate_MxNxP_BLUPs(
  nodule.density.LA.LMM
) %>%
  separate(
    col = Microbiome_Nitrogen_Population,
    c("Microbiome", "Nitrogen", "Population"),
    sep = ":"
  )

## Fixing nodule density
fixing.nodule.density.uncleaned.BLUPs <- calculate_MxNxP_BLUPs(
  fixing.nodule.density.LA.LMM
) %>%
  separate(
    col = Microbiome_Nitrogen_Population,
    c("Microbiome", "Nitrogen", "Population"),
    sep = ":"
  )
```





\newpage
# Measures of Local Adaptation

## Data Management

```{r Data Management: Recoded Microbiome Variable, echo = TRUE}
## Add re-coded Microbiome_Global to calculate global nonlocal effects
# Aboveground biomass
aboveground.biomass.uncleaned.BLUPs$Microbiome_Global <- (
  if_else(aboveground.biomass.uncleaned.BLUPs$Microbiome == "Local", "Local", "Nonlocal_Global")
)

# Belowground biomass
belowground.biomass.uncleaned.BLUPs$Microbiome_Global <- (
  if_else(belowground.biomass.uncleaned.BLUPs$Microbiome == "Local", "Local", "Nonlocal_Global")
)

# Nodule density
nodule.density.uncleaned.BLUPs$Microbiome_Global <- (
  if_else(nodule.density.uncleaned.BLUPs$Microbiome == "Local", "Local", "Nonlocal_Global")
)

# Fixing nodule density
fixing.nodule.density.uncleaned.BLUPs$Microbiome_Global <- (
  if_else(fixing.nodule.density.uncleaned.BLUPs$Microbiome == "Local", "Local", "Nonlocal_Global")
)
```



\newpage
## Aboveground Biomass LA Indices

```{r Local Adaptation Indices: Aboveground Biomass, echo = TRUE}
## Local - Nonlocal_Global
aboveground.biomass.LA.global.data <- aboveground.biomass.uncleaned.BLUPs %>%
  select(Population, Microbiome_Global, Nitrogen, Estimate) %>%
  group_by(Population, Microbiome_Global, Nitrogen) %>%
  summarise(AG_Biomass = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome_Global, values_from = AG_Biomass) %>%
  mutate(AG_Biomass_LA_Global = Local - Nonlocal_Global) %>%
  ungroup()

## Local - Nonlocal_Rural
aboveground.biomass.LA.rural.data <- aboveground.biomass.uncleaned.BLUPs %>%
  select(Population, Microbiome, Nitrogen, Estimate) %>%
  filter(Microbiome != "Nonlocal_U") %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(AG_Biomass = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome, values_from = AG_Biomass) %>%
  mutate(AG_Biomass_LA_Rural = Local - Nonlocal_R) %>%
  ungroup()

## Local - Nonlocal_Urban
aboveground.biomass.LA.urban.data <- aboveground.biomass.uncleaned.BLUPs %>%
  select(Population, Microbiome, Nitrogen, Estimate) %>%
  filter(Microbiome != "Nonlocal_R") %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(AG_Biomass = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome, values_from = AG_Biomass) %>%
  mutate(AG_Biomass_LA_Urban = Local - Nonlocal_U) %>%
  ungroup()
```



\newpage
## Belowground Biomass LA Indices

```{r Local Adaptation Indices: Belowground Biomass, echo = TRUE}
## Local - Nonlocal_Global
belowground.biomass.LA.global.data <- belowground.biomass.uncleaned.BLUPs %>%
  select(Population, Microbiome_Global, Nitrogen, Estimate) %>%
  group_by(Population, Microbiome_Global, Nitrogen) %>%
  summarise(BG_Biomass = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome_Global, values_from = BG_Biomass) %>%
  mutate(BG_Biomass_LA_Global = Local - Nonlocal_Global) %>%
  ungroup()

## Local - Nonlocal_Rural
belowground.biomass.LA.rural.data <- belowground.biomass.uncleaned.BLUPs %>%
  select(Population, Microbiome, Nitrogen, Estimate) %>%
  filter(Microbiome != "Nonlocal_U") %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(BG_Biomass = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome, values_from = BG_Biomass) %>%
  mutate(BG_Biomass_LA_Rural = Local - Nonlocal_R) %>%
  ungroup()

## Local - Nonlocal_Urban
belowground.biomass.LA.urban.data <- belowground.biomass.uncleaned.BLUPs %>%
  select(Population, Microbiome, Nitrogen, Estimate) %>%
  filter(Microbiome != "Nonlocal_R") %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(BG_Biomass = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome, values_from = BG_Biomass) %>%
  mutate(BG_Biomass_LA_Urban = Local - Nonlocal_U) %>%
  ungroup()
```



\newpage
## Nodule Density LA Indices

```{r Local Adaptation Indices: Nodule Density, echo = TRUE}
## Local - Nonlocal_Global
nodule.density.LA.global.data <- nodule.density.uncleaned.BLUPs %>%
  select(Population, Microbiome_Global, Nitrogen, Estimate) %>%
  group_by(Population, Microbiome_Global, Nitrogen) %>%
  summarise(Nod_Density = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome_Global, values_from = Nod_Density) %>%
  mutate(Nod_Density_LA_Global = Local - Nonlocal_Global) %>%
  ungroup()

## Local - Nonlocal_Rural
nodule.density.LA.rural.data <- nodule.density.uncleaned.BLUPs %>%
  select(Population, Microbiome, Nitrogen, Estimate) %>%
  filter(Microbiome != "Nonlocal_U") %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(Nod_Density = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome, values_from = Nod_Density) %>%
  mutate(Nod_Density_LA_Rural = Local - Nonlocal_R) %>%
  ungroup()

## Local - Nonlocal_Urban
nodule.density.LA.urban.data <- nodule.density.uncleaned.BLUPs %>%
  select(Population, Microbiome, Nitrogen, Estimate) %>%
  filter(Microbiome != "Nonlocal_R") %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(Nod_Density = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome, values_from = Nod_Density) %>%
  mutate(Nod_Density_LA_Urban = Local - Nonlocal_U) %>%
  ungroup()
```



\newpage
## Fixing Nodule Density LA Indices

```{r Local Adaptation Indices: Fixing Nodule Density, echo = TRUE}
## Local - Nonlocal_Global
fixing.nodule.density.LA.global.data <- fixing.nodule.density.uncleaned.BLUPs %>%
  select(Population, Microbiome_Global, Nitrogen, Estimate) %>%
  group_by(Population, Microbiome_Global, Nitrogen) %>%
  summarise(Fix_Nod_Density = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome_Global, values_from = Fix_Nod_Density) %>%
  mutate(Fix_Nod_Density_LA_Global = Local - Nonlocal_Global) %>%
  ungroup()

## Local - Nonlocal_Rural
fixing.nodule.density.LA.rural.data <- fixing.nodule.density.uncleaned.BLUPs %>%
  select(Population, Microbiome, Nitrogen, Estimate) %>%
  filter(Microbiome != "Nonlocal_U") %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(Fix_Nod_Density = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome, values_from = Fix_Nod_Density) %>%
  mutate(Fix_Nod_Density_LA_Rural = Local - Nonlocal_R) %>%
  ungroup()

## Local - Nonlocal_Urban
fixing.nodule.density.LA.urban.data <- fixing.nodule.density.uncleaned.BLUPs %>%
  select(Population, Microbiome, Nitrogen, Estimate) %>%
  filter(Microbiome != "Nonlocal_R") %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(Fix_Nod_Density = mean(Estimate), .groups = "keep") %>%
  pivot_wider(names_from = Microbiome, values_from = Fix_Nod_Density) %>%
  mutate(Fix_Nod_Density_LA_Urban = Local - Nonlocal_U) %>%
  ungroup()
```





\newpage
# Correlation Matrices for Local Adaptation Indices


## Local - Nonlocal~Global~ Local Adaptation Correlation Matrix

```{r Local - Nonlocal_Global Correlation Matrix, echo = TRUE}
## Local - Nonlocal_Global data
# Subset local adaptation indices
aboveground.biomass.global <- aboveground.biomass.LA.global.data %>%
  select(Population, Nitrogen, AG_Biomass_LA_Global)
belowground.biomass.global <- belowground.biomass.LA.global.data %>%
  select(Population, Nitrogen, BG_Biomass_LA_Global)
nodule.density.global <- nodule.density.LA.global.data %>%
  select(Population, Nitrogen, Nod_Density_LA_Global)
fixing.nodule.density.global <- fixing.nodule.density.LA.global.data %>%
  select(Population, Nitrogen, Fix_Nod_Density_LA_Global)

# Combine the data
global.local.adaptation.correlation.data <- aboveground.biomass.LA.global.data %>%
  select(Population, Nitrogen) %>%
  left_join(aboveground.biomass.global, by = c("Population", "Nitrogen")) %>%
  left_join(belowground.biomass.global, by = c("Population", "Nitrogen")) %>%
  left_join(nodule.density.global, by = c("Population", "Nitrogen")) %>%
  left_join(fixing.nodule.density.global, by = c("Population", "Nitrogen")) %>%
  drop_na()
```



\newpage
## Local - Nonlocal~Rural~ Local Adaptation Correlation Matrix

```{r Local - Nonlocal_Rural Correlation Matrix, echo = TRUE}
## Local - Nonlocal_Rural data
# Subset local adaptation indices
aboveground.biomass.rural <- aboveground.biomass.LA.rural.data %>%
  select(Population, Nitrogen, AG_Biomass_LA_Rural)
belowground.biomass.rural <- belowground.biomass.LA.rural.data %>%
  select(Population, Nitrogen, BG_Biomass_LA_Rural)
nodule.density.rural <- nodule.density.LA.rural.data %>%
  select(Population, Nitrogen, Nod_Density_LA_Rural)
fixing.nodule.density.rural <- fixing.nodule.density.LA.rural.data %>%
  select(Population, Nitrogen, Fix_Nod_Density_LA_Rural)

# Combine the data
rural.local.adaptation.correlation.data <- aboveground.biomass.LA.rural.data %>%
  select(Population, Nitrogen) %>%
  left_join(aboveground.biomass.rural, by = c("Population", "Nitrogen")) %>%
  left_join(belowground.biomass.rural, by = c("Population", "Nitrogen")) %>%
  left_join(nodule.density.rural, by = c("Population", "Nitrogen")) %>%
  left_join(fixing.nodule.density.rural, by = c("Population", "Nitrogen")) %>%
  drop_na()
```



\newpage
## Local - Nonlocal~Urban~ Local Adaptation Correlation Matrix

```{r Local - Nonlocal_Urban Correlation Matrix, echo = TRUE}
## Local - Nonlocal_Urban data
# Subset local adaptation indices
aboveground.biomass.urban <- aboveground.biomass.LA.urban.data %>%
  select(Population, Nitrogen, AG_Biomass_LA_Urban)
belowground.biomass.urban <- belowground.biomass.LA.urban.data %>%
  select(Population, Nitrogen, BG_Biomass_LA_Urban)
nodule.density.urban <- nodule.density.LA.urban.data %>%
  select(Population, Nitrogen, Nod_Density_LA_Urban)
fixing.nodule.density.urban <- fixing.nodule.density.LA.urban.data %>%
  select(Population, Nitrogen, Fix_Nod_Density_LA_Urban)

# Combine the data
urban.local.adaptation.correlation.data <- aboveground.biomass.LA.urban.data %>%
  select(Population, Nitrogen) %>%
  left_join(aboveground.biomass.urban, by = c("Population", "Nitrogen")) %>%
  left_join(belowground.biomass.urban, by = c("Population", "Nitrogen")) %>%
  left_join(nodule.density.urban, by = c("Population", "Nitrogen")) %>%
  left_join(fixing.nodule.density.urban, by = c("Population", "Nitrogen")) %>%
  drop_na()
```





\newpage
# Export Data

```{r Export Uncleaned BLUPs & Local Adaptation Index Correlation Matrices, include = FALSE}
## Export uncleaned BLUPs
# Aboveground biomass
write_rds(
  aboveground.biomass.uncleaned.BLUPs,
  file = "data/aboveground_biomass_uncleaned_BLUPs.rds"
)
# Belowground biomass
write_rds(
  belowground.biomass.uncleaned.BLUPs,
  file = "data/belowground_biomass_uncleaned_BLUPs.rds"
)
# Nodule density
write_rds(
  nodule.density.uncleaned.BLUPs,
  file = "data/nodule_density_uncleaned_BLUPs.rds"
)
# Fixing nodule density
write_rds(
  fixing.nodule.density.uncleaned.BLUPs,
  file = "data/fixing_nodule_density_uncleaned_BLUPs.rds"
)


## Export the Local - Nonlocal_Global LA Index correlation matrix
write_rds(
  global.local.adaptation.correlation.data,
  file = "data/global_local_adaptation_correlation_data.rds"
)

## Export the Local - Nonlocal_Rural LA Index correlation matrix
write_rds(
  rural.local.adaptation.correlation.data,
  file = "data/rural_local_adaptation_correlation_data.rds"
)

## Export the Local - Nonlocal_Urban LA Index correlation matrix
write_rds(
  urban.local.adaptation.correlation.data,
  file = "data/urban_local_adaptation_correlation_data.rds"
)
```





```{r Save Final Workspace, include = FALSE}
save.image("data_analysis/4-local_adaptation_indices/local_adaptation_indices.RData")
```










\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages,
  booktabs = TRUE,
  caption = "Packages required for data management and analysis."
) %>%
  kable_styling(
    full_width = FALSE,
    latex_options = c("HOLD_position", "striped")
  )
```
