---
title: "TRhizo-localAdaptation"
subtitle: "Cockerham's Test (Global Alternate)"
author: "David Murray-Stoker"
output:
  pdf_document:
    toc: true
    toc_depth: 4
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Packages for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```





\newpage
# Load Packages & Data

```{r Load Packages & Data, echo = TRUE, results = "hide"}
## Load the tidyverse
library(tidyverse)

## Packages for analysis
library(broom)
library(lme4)
library(lmerTest)

## Read in data
biomass.data <- read_rds(file = "data/cleaned_biomass_data.rds")
nodule.data <- read_rds(file = "data/cleaned_nodule_data.rds")

## Recode microbiome levels
biomass.data <- biomass.data %>%
  mutate(Microbiome = if_else(biomass.data$Microbiome == "Local", "Local", "Nonlocal"))
nodule.data <- nodule.data %>%
  mutate(Microbiome = if_else(nodule.data$Microbiome == "Local", "Local", "Nonlocal"))
```





\newpage
# Quantify Genetic Variation

## Data Management

```{r Data Management for Quantifying Genetic Variation, echo = TRUE}
## Aboveground biomass data
# Local
aboveground.biomass.local.data <- biomass.data %>%
  select(Population, Microbiome, Block, Aboveground_Biomass) %>%
  filter(Microbiome == "Local")
# Nonlocal
aboveground.biomass.nonlocal.data <- biomass.data %>%
  select(Population, Microbiome, Block, Aboveground_Biomass) %>%
  filter(Microbiome != "Local")


## Nodule density
# Local | Ambient N
nodule.density.local.ambient.N.data <- nodule.data %>%
  filter(Nitrogen == "Ambient_N") %>%
  select(Population, Microbiome, Block, Nodule_Density) %>%
  filter(Microbiome == "Local")
# Nonlocal | Ambient N
nodule.density.nonlocal.ambient.N.data <- nodule.data %>%
  filter(Nitrogen == "Ambient_N") %>%
  select(Population, Microbiome, Block, Nodule_Density) %>%
  filter(Microbiome != "Local")

# Local | N Addition
nodule.density.local.N.addition.data <- nodule.data %>%
  filter(Nitrogen == "N_Addition") %>%
  select(Population, Microbiome, Block, Nodule_Density) %>%
  filter(Microbiome == "Local")
# Nonlocal | N Addition
nodule.density.nonlocal.N.addition.data <- nodule.data %>%
  filter(Nitrogen == "N_Addition") %>%
  select(Population, Microbiome, Block, Nodule_Density) %>%
  filter(Microbiome != "Local")


## Fixing nodule density data
# Local
fixing.nodule.density.local.data <- nodule.data %>%
  select(Population, Microbiome, Block, Fixing_Nodule_Density) %>%
  filter(Microbiome == "Local")
# Nonlocal
fixing.nodule.density.nonlocal.data <- nodule.data %>%
  select(Population, Microbiome, Block, Fixing_Nodule_Density) %>%
  filter(Microbiome != "Local")
```


\newpage
## Aboveground Biomass

```{r Quantify Genetic Variation: Aboveground Biomass, echo = TRUE}
## Aboveground biomass
# Local
aboveground.biomass.local.Vg.LMM <- lmer(
  sqrt(Aboveground_Biomass) ~ Block + (1 | Population),
  data = aboveground.biomass.local.data,
  REML = TRUE
)

aboveground.biomass.local.Vg.df <- data.frame(VarCorr(aboveground.biomass.local.Vg.LMM)) %>%
  filter(grp == "Population") %>%
  add_column(Microbiome = "Local") %>%
  add_column(Nitrogen = "Combined")

# Nonlocal
aboveground.biomass.nonlocal.Vg.LMM <- lmer(
  sqrt(Aboveground_Biomass) ~ Block + (1 | Population),
  data = aboveground.biomass.nonlocal.data,
  REML = TRUE
)

aboveground.biomass.nonlocal.Vg.df <- data.frame(VarCorr(aboveground.biomass.nonlocal.Vg.LMM)) %>%
  filter(grp == "Population") %>%
  add_column(Microbiome = "Nonlocal") %>%
  add_column(Nitrogen = "Combined")
```


\newpage
## Nodule Density

```{r Quantify Genetic Variation: Nodule Density, echo = TRUE}
## Nodule density
# Ambient N | Local
nodule.density.local.ambient.N.Vg.LMM <- lmer(
  log(Nodule_Density + 1) ~ Block + (1 | Population),
  data = nodule.density.local.ambient.N.data,
  REML = TRUE
)

nodule.density.local.ambient.N.Vg.df <- data.frame(
  VarCorr(nodule.density.local.ambient.N.Vg.LMM)
) %>%
  filter(grp == "Population") %>%
  add_column(Microbiome = "Local") %>%
  add_column(Nitrogen = "Ambient_N")

# Ambient N | Nonlocal
nodule.density.nonlocal.ambient.N.Vg.LMM <- lmer(
  log(Nodule_Density + 1) ~ Block + (1 | Population),
  data = nodule.density.nonlocal.ambient.N.data,
  REML = TRUE
)

nodule.density.nonlocal.ambient.N.Vg.df <- data.frame(
  VarCorr(nodule.density.nonlocal.ambient.N.Vg.LMM)
) %>%
  filter(grp == "Population") %>%
  add_column(Microbiome = "Nonlocal") %>%
  add_column(Nitrogen = "Ambient_N")


# N Addition | Local
nodule.density.local.N.addition.Vg.LMM <- lmer(
  log(Nodule_Density + 1) ~ Block + (1 | Population),
  data = nodule.density.local.N.addition.data,
  REML = TRUE
)

nodule.density.local.N.addition.Vg.df <- data.frame(
  VarCorr(nodule.density.local.N.addition.Vg.LMM)
) %>%
  filter(grp == "Population") %>%
  add_column(Microbiome = "Local") %>%
  add_column(Nitrogen = "N_Addition")

# N Addition | Nonlocal
nodule.density.nonlocal.N.addition.Vg.LMM <- lmer(
  log(Nodule_Density + 1) ~ Block + (1 | Population),
  data = nodule.density.nonlocal.N.addition.data,
  REML = TRUE
)

nodule.density.nonlocal.N.addition.Vg.df <- data.frame(
  VarCorr(nodule.density.nonlocal.N.addition.Vg.LMM)
) %>%
  filter(grp == "Population") %>%
  add_column(Microbiome = "Nonlocal") %>%
  add_column(Nitrogen = "N_Addition")
```


\newpage
## Fixing Nodule Density

```{r Quantify Genetic Variation: Fixing Nodule Density, echo = TRUE}
## Fixing nodule density
# Local
fixing.nodule.density.local.Vg.LMM <- lmer(
  log(Fixing_Nodule_Density + 1) ~ Block + (1 | Population),
  data = fixing.nodule.density.local.data,
  REML = TRUE
)

fixing.nodule.density.local.Vg.df <- data.frame(VarCorr(fixing.nodule.density.local.Vg.LMM)) %>%
  filter(grp == "Population") %>%
  add_column(Microbiome = "Local") %>%
  add_column(Nitrogen = "Combined")

# Nonlocal
fixing.nodule.density.nonlocal.Vg.LMM <- lmer(
  log(Fixing_Nodule_Density + 1) ~ Block + (1 | Population),
  data = fixing.nodule.density.nonlocal.data,
  REML = TRUE
)

fixing.nodule.density.nonlocal.Vg.df <- data.frame(VarCorr(fixing.nodule.density.nonlocal.Vg.LMM)) %>%
  filter(grp == "Population") %>%
  add_column(Microbiome = "Nonlocal") %>%
  add_column(Nitrogen = "Combined")
```




\newpage
## Export Genetic Variation Data

```{r Export Vg Data, echo = TRUE}
## Combine and export data for management in Excel in prep for Cockerham's test
# Bind aboveground biomass data
aboveground.biomass.combined.Vg.data <- bind_rows(
  aboveground.biomass.local.Vg.df,
  aboveground.biomass.nonlocal.Vg.df
)

# Bind nodule density data
nodule.density.combined.Vg.data <- bind_rows(
  nodule.density.local.ambient.N.Vg.df,
  nodule.density.nonlocal.ambient.N.Vg.df,
  nodule.density.local.N.addition.Vg.df,
  nodule.density.nonlocal.N.addition.Vg.df
)

# Bind fixing nodule density data
fixing.nodule.density.combined.Vg.data <- bind_rows(
  fixing.nodule.density.local.Vg.df,
  fixing.nodule.density.nonlocal.Vg.df
)

## Bind all data together
combined.Vg.data <- bind_rows(
  aboveground.biomass.combined.Vg.data,
  nodule.density.combined.Vg.data,
  fixing.nodule.density.combined.Vg.data
) %>%
  add_column(Trait = c(
    rep("Aboveground_Biomass", 2),
    rep("Nodule_Density", 4),
    rep("Fixing_Nodule_Density", 2)
  )) %>%
  select(Trait, Microbiome:Nitrogen, vcov) %>%
  rename(Vg = vcov)

## Export data to prepare for Cockerham's test
write_csv(combined.Vg.data, file = "data/cockerham_data_global_uncleaned.csv")
```










\newpage
# Genetic Correlations

## Data Management


```{r Genetic Correlations: Data Management, echo = TRUE}
## Format data to calculate correlations
full.data <- nodule.data %>%
  full_join(
    biomass.data %>% select(UID, Aboveground_Biomass),
    by = c("UID")
  ) %>%
  select(
    Population:Nitrogen, Aboveground_Biomass, Nodule_Density, Fixing_Nodule_Density
  ) %>%
  drop_na() %>%
  select(
    Population, Microbiome, Nitrogen,
    Aboveground_Biomass:Fixing_Nodule_Density
  )


## Local by Nonlocal data (aboveground biomass and fixing nodule density)
local.by.nonlocal.data <- full.data %>%
  group_by(Population, Microbiome) %>%
  select(-Nodule_Density) %>%
  summarise(
    AG_Biomass = mean(Aboveground_Biomass),
    Fix_Nod_Density = mean(Fixing_Nodule_Density),
    .groups = "keep"
  ) %>%
  ungroup() %>%
  drop_na() %>%
  pivot_wider(names_from = Microbiome, values_from = AG_Biomass:Fix_Nod_Density)


## Nodule density data (N-treatment specific)
# Local by Nonlocal data
nodule.density.local.by.nonlocal.data <- full.data %>%
  group_by(Population, Microbiome, Nitrogen) %>%
  summarise(
    Nod_Density = mean(Nodule_Density),
    .groups = "keep"
  ) %>%
  ungroup() %>%
  pivot_wider(names_from = Microbiome:Nitrogen, values_from = Nod_Density) %>%
  drop_na()
```


\newpage
## Correlations

### Aboveground Biomass & Fixing Nodule Density

```{r Local by Nonlocal Correlations, echo = FALSE}
kable(
  cor(local.by.nonlocal.data %>% select(-1), method = "pearson"),
  booktabs = TRUE,
  digits = 3,
  caption = "Fitness correlations between local and nonlocal-nonlocal for aboveground biomass and fixing nodule density."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
### Nodule Density

```{r Nodule Density: Local by Nonlocal Correlations, echo = FALSE}
kable(
  cor(nodule.density.local.by.nonlocal.data %>% select(-1), method = "pearson"),
  booktabs = TRUE,
  digits = 3,
  caption = "Fitness correlations between local and nonlocal-nonlocal by nitrogen treatment for nodule density."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```










\newpage
# Cockerham's Test

```{r Load Cockerham Data, echo = TRUE}
## Cockerham data
cockerham.global.data <- read_csv(
  "data/cockerham_data_global_cleaned.csv",
  col_types = c("ffnnn"),
  show_col_types = FALSE
)
```



## Set Functions

```{r Functions for Cockerhams Test, echo = TRUE}
## Function for imperfect correlation (page 88, Cockerham 1963)
imperfect_correlation <- function(Vg1, Vg2, Rg) {
  out <- 2 * sqrt(Vg1) * sqrt(Vg2) * (1 - Rg)

  return(out)
}

## Function for heterogeneous variances (page 88, Cockerham 1963)
heterogeneous_variances <- function(Vg1, Vg2) {
  out <- ((sqrt(Vg1) - sqrt(Vg2))^2)

  return(out)
}

## Calculate imperfect correlation values for each row
cockerham.global.data$Crossing <- sapply(1:nrow(cockerham.global.data), FUN = function(r) {
  Vg1 <- cockerham.global.data$Vg1[r]
  Vg2 <- cockerham.global.data$Vg2[r]
  Rg <- cockerham.global.data$Rg[r]

  crossing.value <- imperfect_correlation(Vg1, Vg2, Rg)

  return(crossing.value)
})

## Calculate heterogeneous variance values for each row
cockerham.global.data$Heterogeneous_Variances <- sapply(1:nrow(cockerham.global.data), FUN = function(r) {
  Vg1 <- cockerham.global.data$Vg1[r]
  Vg2 <- cockerham.global.data$Vg2[r]

  heterogeneous.variance.value <- heterogeneous_variances(Vg1, Vg2)

  return(heterogeneous.variance.value)
})
```




\newpage
## Calculations for Cockerham's Test

### Aboveground Biomass

```{r Cockerhams Test: Aboveground Biomass, echo = TRUE}
## Group by trait and calculate sum of imperfect correlation values
# Divide by number of environments*(number of environments - 1) as per Cockerham 1963
aboveground.biomass.crossing <- cockerham.global.data %>%
  filter(Trait == "Aboveground_Biomass") %>%
  summarise(Crossing_Sum = sum(Crossing) / (2 * (2 - 1)))

## Group by trait and calculate sum of heterogeneous variances values
# Divide by number of environments*(number of environments - 1) as per Cockerham 1963
aboveground.biomass.heterogeneous.variance <- cockerham.global.data %>%
  filter(Trait == "Aboveground_Biomass") %>%
  summarise(Hetero_Variance_Sum = sum(Heterogeneous_Variances) / (2 * (2 - 1)))

## Make tibble for aboveground biomass calculation
aboveground.biomass.cockerham.global.data <- tibble(
  Trait = "Aboveground_Biomass",
  aboveground.biomass.crossing,
  aboveground.biomass.heterogeneous.variance
) %>%
  mutate(Total_Variance = Crossing_Sum + Hetero_Variance_Sum) %>%
  mutate(Percent_Crossing = 100 * Crossing_Sum / Total_Variance)
```


\newpage
### Nodule Density

```{r Cockerhams Test: Nodule Density, echo = TRUE}
## Group by trait and calculate sum of imperfect correlation values
# Divide by number of environments*(number of environments - 1) as per Cockerham 1963
nodule.density.crossing <- cockerham.global.data %>%
  filter(Trait == "Nodule_Density") %>%
  summarise(Crossing_Sum = sum(Crossing) / (4 * (4 - 1)))

## Group by trait and calculate sum of heterogeneous variances values
# Divide by number of environments*(number of environments - 1) as per Cockerham 1963
nodule.density.heterogeneous.variance <- cockerham.global.data %>%
  filter(Trait == "Nodule_Density") %>%
  summarise(Hetero_Variance_Sum = sum(Heterogeneous_Variances) / (4 * (4 - 1)))

## Make tibble for Nodule Density calculation
nodule.density.cockerham.global.data <- tibble(
  Trait = "Nodule_Density",
  nodule.density.crossing,
  nodule.density.heterogeneous.variance
) %>%
  mutate(Total_Variance = Crossing_Sum + Hetero_Variance_Sum) %>%
  mutate(Percent_Crossing = 100 * Crossing_Sum / Total_Variance)
```


\newpage
### Fixing Nodule Density

```{r Cockerhams Test: Fixing Nodule Density, echo = TRUE}
## Group by trait and calculate sum of imperfect correlation values
# Divide by number of environments*(number of environments - 1) as per Cockerham 1963
fixing.nodule.density.crossing <- cockerham.global.data %>%
  filter(Trait == "Fixing_Nodule_Density") %>%
  summarise(Crossing_Sum = sum(Crossing) / (2 * (2 - 1)))

## Group by trait and calculate sum of heterogeneous variances values
# Divide by number of environments*(number of environments - 1) as per Cockerham 1963
fixing.nodule.density.heterogeneous.variance <- cockerham.global.data %>%
  filter(Trait == "Fixing_Nodule_Density") %>%
  summarise(Hetero_Variance_Sum = sum(Heterogeneous_Variances) / (2 * (2 - 1)))

## Make tibble for Nodule Density calculation
fixing.nodule.density.cockerham.global.data <- tibble(
  Trait = "Fixing_Nodule_Density",
  fixing.nodule.density.crossing,
  fixing.nodule.density.heterogeneous.variance
) %>%
  mutate(Total_Variance = Crossing_Sum + Hetero_Variance_Sum) %>%
  mutate(Percent_Crossing = 100 * Crossing_Sum / Total_Variance)
```


\newpage
## Results of Cockerham's Tests

```{r Table of Results for Cockerhams Test,echo = FALSE}
kable(
  bind_rows(
    aboveground.biomass.cockerham.global.data,
    nodule.density.cockerham.global.data,
    fixing.nodule.density.cockerham.global.data
  ),
  booktabs = TRUE,
  digits = 5,
  caption = "Results of Cockerham's test for aboveground biomass, nodule density, and fixing nodule density."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





```{r Save the Workspace, include = FALSE}
save.image("data_analysis/3-cockerhams_test/cockerhams_test_alternate_global-workspace.RData")
```










\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages,
  booktabs = TRUE,
  caption = "Packages required for data management and analysis."
) %>%
  kable_styling(
    full_width = FALSE,
    latex_options = c("HOLD_position", "striped")
  )
```
