---
title: "TRhizo-localAdaptation"
subtitle: "Microbiome x Nitrogen Global Analyses (Alternate)"
author: "David Murray-Stoker"
output:
  pdf_document:
    toc: true
    toc_depth: 4
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Packages for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```





\newpage
# Load Packages & Data

```{r Load Packages & Data, echo = TRUE, results = "hide"}
## Load the tidyverse
library(tidyverse)

## Packages for analysis
library(broom)
library(easystats)
library(emmeans)
library(lme4)
library(lmerTest)

## Read in data
biomass.data <- read_rds(file = "data/cleaned_biomass_data.rds")
nodule.data <- read_rds(file = "data/cleaned_nodule_data.rds")

## Recode to Microbiome Global to test for global effects
# Biomass data
biomass.data$Microbiome_Global<- if_else(
  biomass.data$Microbiome == "Local", "Local", "Nonlocal_Global"
)
# Nodule data
nodule.data$Microbiome_Global<- if_else(
  nodule.data$Microbiome == "Local", "Local", "Nonlocal_Global"
)

## Read in workspace
# load("data_analysis/2-microbiome_x_nitrogen-analyses/M_x_N-alternate_global_analyses-workspace.RData")
```





\newpage
# Aboveground Biomass M $\times$ N Model

```{r Aboveground Biomass M x N Model, echo TRUE}
aboveground.biomass.MN.global.LMM <- lmer(
  sqrt(Aboveground_Biomass) ~ Microbiome_Global* Nitrogen
    + (1 | Microbiome_Global:Population)
    + (1 | Nitrogen:Population)
    + (1 | Microbiome_Global:Nitrogen:Population)
    + (1 | Population)
    + (1 | Block),
  data = biomass.data,
  REML = TRUE
)
```


## Check Model Assumptions

\vspace{4pt}

```{r performance Diagnostics: Aboveground Biomass M x N Model Fit, echo = TRUE, eval = FALSE}
## Check model convergence
check_convergence(aboveground.biomass.MN.global.LMM)
# Model converged

## Check for boundary singularity
check_singularity(aboveground.biomass.MN.global.LMM)
# No singularity
```

\vspace{4pt}

```{r performance Diagnostics: Aboveground Biomass M x N Model, echo = TRUE, eval = FALSE}
## Visual assessment of model diagnostics
check_model(aboveground.biomass.MN.global.LMM)
# Visual check = assumptions met

## Check normality of fixed effects (Shapiro-Wilk test)
check_normality(aboveground.biomass.MN.global.LMM, effects = "fixed")
# Suggests statistical non-normality of residuals (P < 0.001)
# Mixed-effects models are robust to this assumption

## Check normality of random effects
check_normality(aboveground.biomass.MN.global.LMM, effects = "random")
# M:P = Good
# N:P = Non-normality detected (P = 0.006)
# M:N:P = Non-normality detected (P = 0.002)
# P = Good
# B = Good

## Check for non-constant variance of residuals (Breusch-Pagan test)
check_heteroscedasticity(aboveground.biomass.MN.global.LMM)
# Statistical evidence for heteroscedasticity (P < 0.001)

## Check for homogeneity of variance (Bartlett test)
check_homogeneity(aboveground.biomass.MN.global.LMM)
# Variances differ between groups (P < 0.001)

## Check for outliers
check_outliers(aboveground.biomass.MN.global.LMM)
# 2 outliers detected
```


\newpage
## Marginal & Conditional R^2^

```{r Marginal and Conditional R-squared: Aboveground Biomass M x N Model, echo = TRUE, results = "hide"}
## Calculate the marginal and conditional R-squared
MuMIn::r.squaredGLMM(aboveground.biomass.MN.global.LMM)
# Marginal = 0.230
# Conditional = 0.394
```

\vspace{4pt}

## ANOVA

```{r ANOVA: Aboveground Biomass M x N Model, echo = TRUE}
## Fit an ANOVA with Type III sums-of-squares
aboveground.biomass.MN.global.LMM.anova <- anova(
  object = aboveground.biomass.MN.global.LMM,
  type = "III",
  ddf = "Kenward-Roger"
)
```

\vspace{4pt}

```{r ANOVA Table: Aboveground Biomass M x N Model, echo = FALSE}
kable(
  aboveground.biomass.MN.global.LMM.anova,
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Aboveground Biomass M x N Model.",
  col.names = c("Sums-of-Squares", "Mean-Square", "Num_df", "Den_df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

## Partial $\eta^2$ for Fixed Effects

```{r Partial Eta-Squared: Aboveground Biomass M x N Model, include = FALSE}
## Calculating partial eta-squared for each factor in the ANOVA
aboveground.biomass.MN.global.LMM.eta.squared <- eta_squared(
  aboveground.biomass.MN.global.LMM.anova,
  partial = TRUE
)
```

\vspace{4pt}

```{r Effect Size Table for Fixed Effects: Aboveground Biomass M x N Model, echo = FALSE}
kable(
  aboveground.biomass.MN.global.LMM.eta.squared,
  booktabs = TRUE,
  digits = 3,
  caption = "Table of the effect sizes for the fixed effects in the Aboveground Biomass M x N Model.",
  col.names = c("Term", "Partial eta-squared", "CI", "CI_low", "CI_high")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## ranova

```{r ranova: Aboveground Biomass M x N Model, echo = TRUE}
## Fit a ranova
aboveground.biomass.MN.global.LMM.ranova <- ranova(
  aboveground.biomass.MN.global.LMM,
  reduce.terms = FALSE
)
```

\vspace{4pt}

```{r ranova Table: Aboveground Biomass M x N Model, echo = FALSE}
kable(
  aboveground.biomass.MN.global.LMM.ranova,
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the ranova for the Aboveground Biomass M x N Model.",
  col.names = c("n_parameters", "log_likelihood", "AIC", "LRT", "df", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

## ICC for Random Effects

```{r ICC For Random Effects: Aboveground Biomass M x N Model, echo = FALSE}
kable(
  icc(aboveground.biomass.MN.global.LMM, by_group = TRUE),
  booktabs = TRUE,
  digits = 3,
  caption = "Table of the effect sizes for the random effects in the Aboveground Biomass M x N Model.",
  col.names = c("Term", "ICC")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## Contrasts

```{r emmeans: Aboveground Biomass, echo = TRUE}
aboveground.biomass.M.emmeans <- emmeans(
  aboveground.biomass.MN.global.LMM,
  specs = pairwise ~ Microbiome_Global,
  weights = "cells",
  adjust = "none"
)

aboveground.biomass.N.emmeans <- emmeans(
  aboveground.biomass.MN.global.LMM,
  specs = pairwise ~ Nitrogen,
  weights = "cells",
  adjust = "none"
)

aboveground.biomass.MxN.emmeans <- emmeans(
  aboveground.biomass.MN.global.LMM,
  specs = pairwise ~ Microbiome_Global| Nitrogen,
  weights = "cells",
  adjust = "none"
)
```

\vspace{4pt}

```{r Post Hoc Comparisons: Aboveground Biomass by Microbiome_Global, echo = FALSE}
kable(
  tidy(aboveground.biomass.M.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the main effect of Microbiome Global in the Aboveground Biomass ANOVA.",
  col.names = c("Term", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Post Hoc Comparisons: Aboveground Biomass by Nitrogen, echo = FALSE}
kable(
  tidy(aboveground.biomass.N.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the main effect of Nitrogen in the Aboveground Biomass ANOVA.",
  col.names = c("Term", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Post Hoc Comparisons: Aboveground Biomass by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  tidy(aboveground.biomass.MxN.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the interaction between Microbiome Global and Nitrogen in the Aboveground Biomass ANOVA.",
  col.names = c("Factor_1", "Factor_2", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## Contrasts (Effect Sizes)

```{r Contrast Effect Sizes: Aboveground Biomass by Microbiome_Global, echo = FALSE}
kable(
  eff_size(aboveground.biomass.M.emmeans,
    sigma = sigma(aboveground.biomass.MN.global.LMM),
    edf = df.residual(aboveground.biomass.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Microbiome Global in the Aboveground Biomass ANOVA.",
  col.names = c("Contrast", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```

\vspace{4pt}

```{r Contrast Effect Sizes: Aboveground Biomass by Nitrogen, echo = FALSE}
kable(
  eff_size(aboveground.biomass.N.emmeans,
    sigma = sigma(aboveground.biomass.MN.global.LMM),
    edf = df.residual(aboveground.biomass.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Nitrogen in the Aboveground Biomass ANOVA.",
  col.names = c("Contrast", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```

\vspace{4pt}

```{r Contrast Effect Sizes: Aboveground Biomass by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  eff_size(aboveground.biomass.MxN.emmeans,
    sigma = sigma(aboveground.biomass.MN.global.LMM),
    edf = df.residual(aboveground.biomass.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Microbiome Global and Nitrogen in the Aboveground Biomass ANOVA.",
  col.names = c("Contrast", "Nitrogen", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```





\newpage
# Belowground Biomass M $\times$ N Model

```{r Belowground Biomass M x N Model, echo TRUE}
belowground.biomass.MN.global.LMM <- lmer(
  sqrt(Belowground_Biomass) ~ Microbiome_Global* Nitrogen
    + (1 | Population)
    + (1 | Block),
  data = biomass.data,
  REML = TRUE
)
```


## Check Model Assumptions

```{r performance Diagnostics: Belowground Biomass M x N Model Fit, echo = TRUE, eval = FALSE}
## Check model convergence
check_convergence(belowground.biomass.MN.global.LMM)
# Model converged

## Check for boundary singularity
check_singularity(belowground.biomass.MN.global.LMM)
# No singularity
```

\vspace{4pt}

```{r performance Diagnostics: Belowground Biomass M x N Model, echo = TRUE, eval = FALSE}
## Visual assessment of model diagnostics
check_model(belowground.biomass.MN.global.LMM)
# Visual check = assumptions met

## Check normality of fixed effects (Shapiro-Wilk test)
check_normality(belowground.biomass.MN.global.LMM, effects = "fixed")
# Suggests statistical non-normality of residuals (P < 0.001)
# Mixed-effects models are robust to this assumption

## Check normality of random effects
check_normality(belowground.biomass.MN.global.LMM, effects = "random")
# P = Good
# B = Good

## Check for non-constant variance of residuals (Breusch-Pagan test)
check_heteroscedasticity(belowground.biomass.MN.global.LMM)
# Statistical evidence for heteroscedasticity (P < 0.001)

## Check for homogeneity of variance (Bartlett test)
check_homogeneity(belowground.biomass.MN.global.LMM)
# Variances differ between groups (P < 0.001)

## Check for outliers
check_outliers(belowground.biomass.MN.global.LMM)
# No outliers detected
```


\newpage
## Marginal & Conditional R^2^

```{r Marginal and Conditional R-squared: Belowground Biomass M x N Model, echo = TRUE, results = "hide"}
## Calculate the marginal and conditional R-squared
MuMIn::r.squaredGLMM(belowground.biomass.MN.global.LMM)
# Marginal = 0.288
# Conditional = 0.373
```

\vspace{4pt}

## ANOVA

```{r ANOVA: Belowground Biomass M x N Model, echo = TRUE}
## Fit an ANOVA with Type III sums-of-squares
belowground.biomass.MN.global.LMM.anova <- anova(
  object = belowground.biomass.MN.global.LMM,
  type = "III",
  ddf = "Kenward-Roger"
)
```

\vspace{4pt}

```{r ANOVA Table: Belowground Biomass M x N Model, echo = FALSE}
kable(
  belowground.biomass.MN.global.LMM.anova,
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Belowground Biomass M x N Model.",
  col.names = c("Sums-of-Squares", "Mean-Square", "Num_df", "Den_df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

## Partial $\eta^2$ for Fixed Effects

```{r Partial Eta-Squared: Belowground Biomass M x N Model, include = FALSE}
## Calculating partial eta-squared for each factor in the ANOVA
belowground.biomass.MN.global.LMM.eta.squared <- eta_squared(
  belowground.biomass.MN.global.LMM.anova,
  partial = TRUE
)
```

\vspace{4pt}

```{r Effect Size Table for Fixed Effects: Belowground Biomass M x N Model, echo = FALSE}
kable(
  belowground.biomass.MN.global.LMM.eta.squared,
  booktabs = TRUE,
  digits = 3,
  caption = "Table of the effect sizes for the fixed effects in the Belowground Biomass M x N Model.",
  col.names = c("Term", "Partial eta-squared", "CI", "CI_low", "CI_high")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## ranova

```{r ranova: Belowground Biomass M x N Model, echo = TRUE}
## Fit a ranova
belowground.biomass.MN.global.LMM.ranova <- ranova(
  belowground.biomass.MN.global.LMM,
  reduce.terms = FALSE
)
```

\vspace{4pt}

```{r ranova Table: Belowground Biomass M x N Model, echo = FALSE}
kable(
  belowground.biomass.MN.global.LMM.ranova,
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the ranova for the Belowground Biomass M x N Model.",
  col.names = c("n_parameters", "log_likelihood", "AIC", "LRT", "df", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

## ICC for Random Effects

```{r ICC For Random Effects: Belowground Biomass M x N Model, echo = FALSE}
kable(
  icc(belowground.biomass.MN.global.LMM, by_group = TRUE),
  booktabs = TRUE,
  digits = 3,
  caption = "Table of the effect sizes for the random effects in the Belowground Biomass M x N Model.",
  col.names = c("Term", "ICC")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## Contrasts

```{r emmeans: Belowground Biomass, echo = TRUE}
belowground.biomass.M.emmeans <- emmeans(
  belowground.biomass.MN.global.LMM,
  specs = pairwise ~ Microbiome_Global,
  weights = "cells",
  adjust = "none"
)

belowground.biomass.N.emmeans <- emmeans(
  belowground.biomass.MN.global.LMM,
  specs = pairwise ~ Nitrogen,
  weights = "cells",
  adjust = "none"
)

belowground.biomass.MxN.emmeans <- emmeans(
  belowground.biomass.MN.global.LMM,
  specs = pairwise ~ Microbiome_Global| Nitrogen,
  weights = "cells",
  adjust = "none"
)
```

\vspace{4pt}

```{r Post Hoc Comparisons: Belowground Biomass by Microbiome_Global, echo = FALSE}
kable(
  tidy(belowground.biomass.M.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the main effect of Microbiome Global in the Belowground Biomass ANOVA.",
  col.names = c("Term", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Post Hoc Comparisons: Belowground Biomass by Nitrogen, echo = FALSE}
kable(
  tidy(belowground.biomass.N.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the main effect of Nitrogen in the Belowground Biomass ANOVA.",
  col.names = c("Term", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Post Hoc Comparisons: Belowground Biomass by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  tidy(belowground.biomass.MxN.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the interaction between Microbiome Global and Nitrogen in the Belowground Biomass ANOVA.",
  col.names = c("Factor_1", "Factor_2", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## Contrasts (Effect Sizes)

```{r Contrast Effect Sizes: Belowground Biomass by Microbiome_Global, echo = FALSE}
kable(
  eff_size(belowground.biomass.M.emmeans,
    sigma = sigma(belowground.biomass.MN.global.LMM),
    edf = df.residual(belowground.biomass.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Microbiome Global in the Belowground Biomass ANOVA.",
  col.names = c("Contrast", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```

\vspace{4pt}

```{r Contrast Effect Sizes: Belowground Biomass by Nitrogen, echo = FALSE}
kable(
  eff_size(belowground.biomass.N.emmeans,
    sigma = sigma(belowground.biomass.MN.global.LMM),
    edf = df.residual(belowground.biomass.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Nitrogen in the Belowground Biomass ANOVA.",
  col.names = c("Contrast", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```

\vspace{4pt}

```{r Contrast Effect Sizes: Belowground Biomass by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  eff_size(belowground.biomass.MxN.emmeans,
    sigma = sigma(belowground.biomass.MN.global.LMM),
    edf = df.residual(belowground.biomass.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Microbiome Global and Nitrogen in the Belowground Biomass ANOVA.",
  col.names = c("Contrast", "Nitrogen", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```




\newpage
# Nodule Density M $\times$ N Model

```{r Nodule Density M x N Model, echo TRUE}
nodule.density.MN.global.LMM <- lmer(
  log(Nodule_Density + 1) ~ Microbiome_Global* Nitrogen
    + (1 | Microbiome_Global:Population)
    + (1 | Nitrogen:Population)
    + (1 | Microbiome:Nitrogen:Population)
    + (1 | Population)
    + (1 | Block),
  data = nodule.data,
  REML = TRUE
)
```


## Check Model Assumptions

```{r performance Diagnostics: Nodule Density M x N Model Fit, echo = TRUE, eval = FALSE}
## Check model convergence
check_convergence(nodule.density.MN.global.LMM)
# Model converged

## Check for boundary singularity
check_singularity(nodule.density.MN.global.LMM)
# Singularity
```

\vspace{4pt}

```{r performance Diagnostics: Nodule Density M x N Model, echo = TRUE, eval = FALSE}
## Visual assessment of model diagnostics
check_model(nodule.density.MN.global.LMM)
# Visual check = assumptions met

## Check normality of fixed effects (Shapiro-Wilk test)
check_normality(nodule.density.MN.global.LMM, effects = "fixed")
# Suggests statistical non-normality of residuals (P < 0.001)
# Mixed-effects models are robust to this assumption

## Check normality of random effects
check_normality(nodule.density.MN.global.LMM, effects = "random")
# M:P = Good
# N:P = Good
# M:N:P = Good
# P = Good
# B = Good

## Check for non-constant variance of residuals (Breusch-Pagan test)
check_heteroscedasticity(nodule.density.MN.global.LMM)
# Statistical evidence for heteroscedasticity (P < 0.001)

## Check for homogeneity of variance (Bartlett test)
check_homogeneity(nodule.density.MN.global.LMM)
# Variances differ between groups (P < 0.001)

## Check for outliers
check_outliers(nodule.density.MN.global.LMM)
# 6 outliers detected
```


\newpage
## Marginal & Conditional R^2^

```{r Marginal and Conditional R-squared: Nodule Density M x N Model, echo = TRUE, results = "hide"}
## Calculate the marginal and conditional R-squared
MuMIn::r.squaredGLMM(nodule.density.MN.global.LMM)
# Marginal = 0.055
# Conditional = 0.263
```

\vspace{4pt}

## ANOVA

```{r ANOVA: Nodule Density M x N Model, echo = TRUE}
## Fit an ANOVA with Type III sums-of-squares
nodule.density.MN.global.LMM.anova <- anova(
  object = nodule.density.MN.global.LMM,
  type = "III",
  ddf = "Kenward-Roger"
)
```

\vspace{4pt}

```{r ANOVA Table: Nodule Density M x N Model, echo = FALSE}
kable(
  nodule.density.MN.global.LMM.anova,
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Nodule Density M x N Model.",
  col.names = c("Sums-of-Squares", "Mean-Square", "Num_df", "Den_df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

## Partial $\eta^2$ for Fixed Effects

```{r Partial Eta-Squared: Nodule Density M x N Model, include = FALSE}
## Calculating partial eta-squared for each factor in the ANOVA
nodule.density.MN.global.LMM.eta.squared <- eta_squared(
  nodule.density.MN.global.LMM.anova,
  partial = TRUE
)
```

\vspace{4pt}

```{r Effect Size Table for Fixed Effects: Nodule Density M x N Model, echo = FALSE}
kable(
  nodule.density.MN.global.LMM.eta.squared,
  booktabs = TRUE,
  digits = 3,
  caption = "Table of the effect sizes for the fixed effects in the Nodule Density M x N Model.",
  col.names = c("Term", "Partial eta-squared", "CI", "CI_low", "CI_high")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## ranova

```{r ranova: Nodule Density M x N Model, echo = TRUE}
## Fit a ranova
nodule.density.MN.global.LMM.ranova <- ranova(
  nodule.density.MN.global.LMM,
  reduce.terms = FALSE
)
```

\vspace{4pt}

```{r ranova Table: Nodule Density M x N Model, echo = FALSE}
kable(
  nodule.density.MN.global.LMM.ranova,
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the ranova for the Nodule Density M x N Model.",
  col.names = c("n_parameters", "log_likelihood", "AIC", "LRT", "df", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

## ICC for Random Effects

```{r ICC For Random Effects: Nodule Density M x N Model, echo = FALSE}
## Total random variance
nodule.density.random.variance <- (
  sum(7.745965e-03 + 1.969510e-10 + 0 + 2.871787e-03 + 2.200630e-04 + 3.834e-02)
)

nodule.density.MN.global.ICC <- tibble(
  Term = c(
  	"Microbiome:Population", "Nitrogen:Population", "Microbiome:Nitrogen:Population",
  	"Population", "Block"
  ),
  ICC = c(
    0 / nodule.density.random.variance,
    1.969510e-10 / nodule.density.random.variance,
    7.745965e-03 / nodule.density.random.variance,
    2.871787e-03 / nodule.density.random.variance,
    2.200630e-04 / nodule.density.random.variance
  )
)

kable(
  nodule.density.MN.global.ICC,
  booktabs = TRUE,
  digits = 3,
  caption = "Table of the effect sizes for the random effects in the Nodule Density M x N Model."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## Contrasts

```{r emmeans: Nodule Density, echo = TRUE}
nodule.density.M.emmeans <- emmeans(
  nodule.density.MN.global.LMM,
  specs = pairwise ~ Microbiome_Global,
  weights = "cells",
  adjust = "none"
)

nodule.density.N.emmeans <- emmeans(
  nodule.density.MN.global.LMM,
  specs = pairwise ~ Nitrogen,
  weights = "cells",
  adjust = "none"
)

nodule.density.MxN.emmeans <- emmeans(
  nodule.density.MN.global.LMM,
  specs = pairwise ~ Microbiome_Global| Nitrogen,
  weights = "cells",
  adjust = "none"
)
```

\vspace{4pt}

```{r Post Hoc Comparisons: Nodule Density by Microbiome_Global, echo = FALSE}
kable(
  tidy(nodule.density.M.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the main effect of Microbiome Global in the Nodule Density ANOVA.",
  col.names = c("Term", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Post Hoc Comparisons: Nodule Density by Nitrogen, echo = FALSE}
kable(
  tidy(nodule.density.N.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the main effect of Nitrogen in the Nodule Density ANOVA.",
  col.names = c("Term", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Post Hoc Comparisons: Nodule Density by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  tidy(nodule.density.MxN.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the interaction between Microbiome Global and Nitrogen in the Nodule Density ANOVA.",
  col.names = c("Factor_1", "Factor_2", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## Contrasts (Effect Sizes)

```{r Contrast Effect Sizes: Nodule Density by Microbiome_Global, echo = FALSE}
kable(
  eff_size(nodule.density.M.emmeans,
    sigma = sigma(nodule.density.MN.global.LMM),
    edf = df.residual(nodule.density.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Microbiome Global in the Nodule Density ANOVA.",
  col.names = c("Contrast", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```

\vspace{4pt}

```{r Contrast Effect Sizes: Nodule Density by Nitrogen, echo = FALSE}
kable(
  eff_size(nodule.density.N.emmeans,
    sigma = sigma(nodule.density.MN.global.LMM),
    edf = df.residual(nodule.density.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Nitrogen in the Nodule Density ANOVA.",
  col.names = c("Contrast", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```

\vspace{4pt}

```{r Contrast Effect Sizes: Nodule Density by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  eff_size(nodule.density.MxN.emmeans,
    sigma = sigma(nodule.density.MN.global.LMM),
    edf = df.residual(nodule.density.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Microbiome Global and Nitrogen in the Nodule Density ANOVA.",
  col.names = c("Contrast", "Nitrogen", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```





\newpage
# Fixing Nodule Density M $\times$ N Model

```{r Fixing Nodule Density M x N Model, echo TRUE}
fixing.nodule.density.MN.global.LMM <- lmer(
  log(Fixing_Nodule_Density + 1) ~ Microbiome_Global* Nitrogen
    + (1 | Microbiome_Global:Population)
    + (1 | Nitrogen:Population)
    + (1 | Population)
    + (1 | Block),
  data = nodule.data,
  REML = TRUE
)
```


## Check Model Assumptions

```{r performance Diagnostics: Fixing Nodule Density M x N Model Fit, echo = TRUE, eval = FALSE}
## Check model convergence
check_convergence(fixing.nodule.density.MN.global.LMM)
# Model converged

## Check for boundary singularity
check_singularity(fixing.nodule.density.MN.global.LMM)
# No singularity
```

\vspace{4pt}

```{r performance Diagnostics: Fixing Nodule Density M x N Model, echo = TRUE, eval = FALSE}
## Visual assessment of model diagnostics
check_model(fixing.nodule.density.MN.global.LMM)
# Visual check = assumptions met

## Check normality of fixed effects (Shapiro-Wilk test)
check_normality(fixing.nodule.density.MN.global.LMM, effects = "fixed")
# Suggests statistical non-normality of residuals (P < 0.001)
# Mixed-effects models are robust to this assumption

## Check normality of random effects
check_normality(fixing.nodule.density.MN.global.LMM, effects = "random")
# M:P = Good
# N:P = Good
# P = Non-normality detected (P < 0.001)
# B = Good

## Check for non-constant variance of residuals (Breusch-Pagan test)
check_heteroscedasticity(fixing.nodule.density.MN.global.LMM)
# Statistical evidence for heteroscedasticity (P < 0.001)

## Check for homogeneity of variance (Bartlett test)
check_homogeneity(fixing.nodule.density.MN.global.LMM)
# Variances differ between groups (P < 0.001)

## Check for outliers
check_outliers(fixing.nodule.density.MN.global.LMM)
# 1 outlier detected
```


\newpage
## Marginal & Conditional R^2^

```{r Marginal and Conditional R-squared: Fixing Nodule Density M x N Model, echo = TRUE, results = "hide"}
## Calculate the marginal and conditional R-squared
MuMIn::r.squaredGLMM(fixing.nodule.density.MN.global.LMM)
# Marginal = 0.041
# Conditional = 0.162
```

\vspace{4pt}

## ANOVA

```{r ANOVA: Fixing Nodule Density M x N Model, echo = TRUE}
## Fit an ANOVA with Type III sums-of-squares
fixing.nodule.density.MN.global.LMM.anova <- anova(
  object = fixing.nodule.density.MN.global.LMM,
  type = "III",
  ddf = "Kenward-Roger"
)
```

\vspace{4pt}

```{r ANOVA Table: Fixing Nodule Density M x N Model, echo = FALSE}
kable(
  fixing.nodule.density.MN.global.LMM.anova,
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Fixing Nodule Density M x N Model.",
  col.names = c("Sums-of-Squares", "Mean-Square", "Num_df", "Den_df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

## Partial $\eta^2$ for Fixed Effects

```{r Partial Eta-Squared: Fixing Nodule Density M x N Model, include = FALSE}
## Calculating partial eta-squared for each factor in the ANOVA
fixing.nodule.density.MN.global.LMM.eta.squared <- eta_squared(
  fixing.nodule.density.MN.global.LMM.anova,
  partial = TRUE
)
```

\vspace{4pt}

```{r Effect Size Table for Fixed Effects: Fixing Nodule Density M x N Model, echo = FALSE}
kable(
  fixing.nodule.density.MN.global.LMM.eta.squared,
  booktabs = TRUE,
  digits = 3,
  caption = "Table of the effect sizes for the fixed effects in the Fixing Nodule Density M x N Model.",
  col.names = c("Term", "Partial eta-squared", "CI", "CI_low", "CI_high")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## ranova

```{r ranova: Fixing Nodule Density M x N Model, echo = TRUE}
## Fit a ranova
fixing.nodule.density.MN.global.LMM.ranova <- ranova(
  fixing.nodule.density.MN.global.LMM,
  reduce.terms = FALSE
)
```

\vspace{4pt}

```{r ranova Table: Fixing Nodule Density M x N Model, echo = FALSE}
kable(
  fixing.nodule.density.MN.global.LMM.ranova,
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the ranova for the Fixing Nodule Density M x N Model.",
  col.names = c("n_parameters", "log_likelihood", "AIC", "LRT", "df", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

## ICC for Random Effects

```{r ICC For Random Effects: Fixing Nodule Density M x N Model, echo = FALSE}
kable(
  icc(fixing.nodule.density.MN.global.LMM, by_group = TRUE),
  booktabs = TRUE,
  digits = 3,
  caption = "Table of the effect sizes for the random effects in the Fixing Nodule Density M x N Model.",
  col.names = c("Term", "ICC")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## Contrasts

```{r emmeans: Fixing Nodule Density, echo = TRUE}
fixing.nodule.density.M.emmeans <- emmeans(
  fixing.nodule.density.MN.global.LMM,
  specs = pairwise ~ Microbiome_Global,
  weights = "cells",
  adjust = "none"
)

fixing.nodule.density.N.emmeans <- emmeans(
  fixing.nodule.density.MN.global.LMM,
  specs = pairwise ~ Nitrogen,
  weights = "cells",
  adjust = "none"
)

fixing.nodule.density.MxN.emmeans <- emmeans(
  fixing.nodule.density.MN.global.LMM,
  specs = pairwise ~ Microbiome_Global| Nitrogen,
  weights = "cells",
  adjust = "none"
)
```

\vspace{4pt}

```{r Post Hoc Comparisons: Fixing Nodule Density by Microbiome_Global, echo = FALSE}
kable(
  tidy(fixing.nodule.density.M.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the main effect of Microbiome Global in the Fixing Nodule Density ANOVA.",
  col.names = c("Term", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Post Hoc Comparisons: Fixing Nodule Density by Nitrogen, echo = FALSE}
kable(
  tidy(fixing.nodule.density.N.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the main effect of Nitrogen in the Fixing Nodule Density ANOVA.",
  col.names = c("Term", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Post Hoc Comparisons: Fixing Nodule Density by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  tidy(fixing.nodule.density.MxN.emmeans$contrasts),
  booktabs = TRUE,
  digits = 3,
  caption = "Post-hoc comparisons of the interaction between Microbiome Global and Nitrogen in the Fixing Nodule Density ANOVA.",
  col.names = c("Factor_1", "Factor_2", "Contrast", "Null Value", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage
## Contrasts (Effect Sizes)

```{r Contrast Effect Sizes: Fixing Nodule Density by Microbiome_Global, echo = FALSE}
kable(
  eff_size(fixing.nodule.density.M.emmeans,
    sigma = sigma(fixing.nodule.density.MN.global.LMM),
    edf = df.residual(fixing.nodule.density.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Microbiome Global in the Fixing Nodule Density ANOVA.",
  col.names = c("Contrast", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```

\vspace{4pt}

```{r Contrast Effect Sizes: Fixing Nodule Density by Nitrogen, echo = FALSE}
kable(
  eff_size(fixing.nodule.density.N.emmeans,
    sigma = sigma(fixing.nodule.density.MN.global.LMM),
    edf = df.residual(fixing.nodule.density.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Nitrogen in the Fixing Nodule Density ANOVA.",
  col.names = c("Contrast", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```

\vspace{4pt}

```{r Contrast Effect Sizes: Fixing Nodule Density by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  eff_size(fixing.nodule.density.MxN.emmeans,
    sigma = sigma(fixing.nodule.density.MN.global.LMM),
    edf = df.residual(fixing.nodule.density.MN.global.LMM)
  ),
  booktabs = TRUE,
  digits = 3,
  caption = "Effect sizes for the constrasts by Microbiome Global and Nitrogen in theFixing  Nodule Density ANOVA.",
  col.names = c("Contrast", "Nitrogen", "Cohen's d", "SE", "df", "CI Lower", "CI Upper")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down"))
```





\newpage
# Supplementary: Estimated Marginal Means


## Aboveground Biomass M $\times$ N Model

```{r Marginal Means: Aboveground Biomass by Microbiome_Global, echo = FALSE}
kable(
  tidy(aboveground.biomass.M.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the main effect of Microbiome Global in the Aboveground Biomass ANOVA.",
  col.names = c("Microbiome_Global", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Marginal Means: Aboveground Biomass by Nitrogen, echo = FALSE}
kable(
  tidy(aboveground.biomass.N.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the main effect of Nitrogen in the Aboveground Biomass ANOVA.",
  col.names = c("Nitrogen", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Marginal Means: Aboveground Biomass by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  tidy(aboveground.biomass.MxN.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the interaction between Microbiome Global and Nitrogen in the Aboveground Biomass ANOVA.",
  col.names = c("Microbiome_Global", "Nitrogen", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Belowground Biomass M $\times$ N Model

```{r Marginal Means: Belowground Biomass by Microbiome_Global, echo = FALSE}
kable(
  tidy(belowground.biomass.M.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the main effect of Microbiome Global in the Belowground Biomass ANOVA.",
  col.names = c("Microbiome_Global", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Marginal Means: Belowground Biomass by Nitrogen, echo = FALSE}
kable(
  tidy(belowground.biomass.N.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the main effect of Nitrogen in the Belowground Biomass ANOVA.",
  col.names = c("Nitrogen", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Marginal Means: Belowground Biomass by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  tidy(belowground.biomass.MxN.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the interaction between Microbiome Global and Nitrogen in the Belowground Biomass ANOVA.",
  col.names = c("Microbiome_Global", "Nitrogen", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Nodule Density M $\times$ N Model

```{r Marginal Means: Nodule Density by Microbiome_Global, echo = FALSE}
kable(
  tidy(nodule.density.M.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the main effect of Microbiome Global in the Nodule Density ANOVA.",
  col.names = c("Microbiome_Global", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Marginal Means: Nodule Density by Nitrogen, echo = FALSE}
kable(
  tidy(nodule.density.N.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the main effect of Nitrogen in the Nodule Density ANOVA.",
  col.names = c("Nitrogen", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Marginal Means: Nodule Density by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  tidy(nodule.density.MxN.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the interaction between Microbiome Global and Nitrogen in the Nodule Density ANOVA.",
  col.names = c("Microbiome_Global", "Nitrogen", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```



\newpage
## Fixing Nodule Density M $\times$ N Model

```{r Marginal Means: Fixing Nodule Density by Microbiome_Global, echo = FALSE}
kable(
  tidy(fixing.nodule.density.M.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the main effect of Microbiome Global in the Fixing Nodule Density ANOVA.",
  col.names = c("Microbiome_Global", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Marginal Means: Fixing Nodule Density by Nitrogen, echo = FALSE}
kable(
  tidy(fixing.nodule.density.N.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the main effect of Nitrogen in the Fixing Nodule Density ANOVA.",
  col.names = c("Nitrogen", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{4pt}

```{r Marginal Means: Fixing Nodule Density by Microbiome Global and Nitrogen, echo = FALSE}
kable(
  tidy(fixing.nodule.density.MxN.emmeans$emmeans),
  booktabs = TRUE,
  digits = 3,
  caption = "Estimated marginal means of the interaction between Microbiome Global and Nitrogen in the Fixing Nodule Density ANOVA.",
  col.names = c("Microbiome_Global", "Nitrogen", "Estimate", "SE", "df", "t", "P")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Export Data

```{r Export LMMs, echo = TRUE}
## Export the aboveground biomass LMM
write_rds(
  aboveground.biomass.MN.global.LMM,
  file = "data/aboveground_biomass_MN_global_LMM.rds"
)

## Export the belowground biomass LMM
write_rds(
  belowground.biomass.MN.global.LMM,
  file = "data/belowground_biomass_MN_global_LMM.rds"
)

## Export the nodule density LMM
write_rds(
  nodule.density.MN.global.LMM,
  file = "data/nodule_density_MN_global_LMM.rds"
)

## Export the fixing nodule density LMM
write_rds(
  fixing.nodule.density.MN.global.LMM,
  file = "data/fixing_nodule_density_MN_global_LMM.rds"
)
```










```{r Save the Workspace, include = FALSE}
save.image("data_analysis/2-microbiome_x_nitrogen-analyses/M_x_N-alternate_global_analyses-workspace.RData")
```










\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages,
  booktabs = TRUE,
  caption = "Packages required for data management and analysis."
) %>%
  kable_styling(
    full_width = FALSE,
    latex_options = c("HOLD_position", "striped")
  )
```
